Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2014-09-22 draft_lm1.tex
added more refs

Multiple factors contribute to the dificulty in estimating the number of 
susceptibles in the population, first and foremost is the fact that dengue 
confers permanente immunity within serotypes but with only short-lived 
cross-immunity. Secondly, there are a larger number of asymptomatic cases in 
any epidemic, which nevertheless acquire immunity. Lastly Demography and 
migrations affect the number of susceptible in ways which are not easy to 
determine.

>>>>

Multiple factors contribute to the dificulty in estimating the number of 
susceptibles in the population, first and foremost is the fact that dengue 
confers permanente immunity within serotypes but with only short-lived 
cross-immunity. Secondly, there are a larger number of asymptomatic cases in 
any epidemic, which nevertheless acquire immunity, Thirdly, under-reporting is 
a serious issue in Brazil. Duarte and Franca\cite{duarte_data_2006}, estimated 
the sensitivity of dengue reporting in Belo-Horizonte, Brazil to be of 63\%, 
meaning that aproximately 37\% of the cases go unreported. Lastly, demography 
and migrations affect the number of susceptible in ways which are not easy to 
determine.
